---
title: "Bootstrap"
author: "Clinton Tippett"
date: "June 6, 2016"
output: word_document
---

# I am going to create four vectors, two which will have a normal distribution and two an exponential distribution. I will then use these vectors to perform the bootstrap technique in order to show examples of Central Limit Theorem.

```{r}
sampx <- rnorm(50,10,5)
sampy <- rnorm(4500,385,20)
hist(sampx)
hist(sampy)
```

# I created two vectors with a normal distribution. Each of these are unique, and contain vastly different sizes and amounts.
# 'sampx' and 'sampy' are the names of the two vectors. 

```{r}
xampx <- rexp(50, 1/20)
hist(xampx)
xampy <- rexp(4500, 1/500)
hist(xampy)
```

# Here I have created two new vectors 'xampx' and 'xampy'.
# These two vectors are of an exponential distribution 
# I used to 'rexp' function to generate the numbers with a defined mean.
# I then tested the vectors using a histogram to verify that the distribution was indeed exponential.
# Now that we have four vectors, two of normal and two of exponential dist, we can apply bootstap technique to verify that the outcomes will follow central limit theorem
# Next, I am going to use the loop function to produce several automated iterations and calculate the means of each iterations

```{r}
R <- 1000
bootmean <- numeric(R)
for (i in 1:R) {
bootsample <- sample(sampx, size=length(sampx), replace=TRUE)
bootmean[i] <- mean(bootsample)}
```

# now, I am going to check the normality of the result 'bootmean'

```{r}
hist(bootmean)
```

# as expected, the results from bootmean for a normal distribution.
# this was doubly expected -- The original vector from which the sample was obtained was a normal distribution
# Now I will repeat the process for 'sampy', the other normal dist vector, and check the outcome

```{r}
bootmean2 <- numeric(R)
for (i in 1:R) {
  bootsample2 <- sample(sampy, size=length(sampy), replace=TRUE)
  bootmean2[i] <- mean(bootsample2)}

hist(bootmean2)
```

# Again, a normal distribution is realized. 
# Next, I will repeat the procedures for both of the exponential dist vectors 'xampx' and 'xampy'

```{r}
bootmean3 <- numeric(R)
for (i in 1:R){
  bootsample3 <- sample(xampx, size=length(xampx), replace=TRUE)
  bootmean3[i] <- mean(bootsample3)}

hist(bootmean3)
```

# Here are the results from the vector 'xampx', which is an exponential distribution.
# We can see that the histogram approaches normality
# This helps visualize the concept of central limit theorem
# Even though our original data set was of exponential dist, when we sampled from that over and over, the plotted means produce a histogram that approaches normality.
# Now, I will show this concept again with the other exponential dist vector 'xampy'

```{r}
bootmean4 <- numeric(R)
for (i in 1:R){
  bootsample4 <- sample(xampy, size=length(xampy), replace=TRUE)
  bootmean4[i] <- mean(bootsample4)}

hist(bootmean4)
```

# bootstrap success!
# again, we see that the results produce a histogram that approaches normality. These two histograms are quite different, and shows how regardless of the distribution of the original data, bootstrapping will yield a normal dist 

```{r}
attach(mtcars)
par(mfrow=c(1,2))
hist(xampy)
hist(bootmean4)
```

git remote add origin git@github.com:CKTippett/bootstrap.git 
git push -u origin master
